Extended Data

### 2022-06-01 doc/manuscript/Dow_manuscript_Nature.Rmd
@teixeirak adding version no. & code location

<!--Hypothesis testing -->
Correlation between the dendrometer band-derived growth parameters (*DOY~25~*, *DOY~50~*, *DOY~75~*, *L~pgs~*, *g~max~*, and *∆DBH*, Fig. `r schematic_summary`) and _CTW_ *T~max~* (at weekly or monthly resolution, as described above) were assessed using a linear mixed model in a hierarchical Bayesian framework.
Analyses were run for both *T~max~* and *T~min~*, with qualitatively similar results, but we present only results for *T~max~*, which had overall stronger correlation with growth parameters. 
Mixed effects models were used to test the response of growth parameters to fixed effects of xylem porosity and mean *T~max~* (or *T~min~*) during the _CTW_, along with random effects of species and of individual tree. 
We ran separate models for each site, and for the response of all growth parameters to *T~max~* (or *T~min~*). 
This mixed-effect model was run within a hierarchical Bayesian framework and fit using the `rstanarm` R interface to the Stan programming language[@gabry_rstanarm_2020;@standevelopmentteam_stan_2019]. 
In all cases unless otherwise specified, all prior distributions are set to be the weakly informative defaults. 
<!--
More information on rstanarm's default weakly informative priors:
https://cran.r-project.org/web/packages/rstanarm/vignettes/priors.html#default-weakly-informative-prior-distributions
-->

>>>>

<!--Hypothesis testing -->
Correlation between the dendrometer band-derived growth parameters (*DOY~25~*, *DOY~50~*, *DOY~75~*, *L~pgs~*, *g~max~*, and *∆DBH*, Fig. `r schematic_summary`) and _CTW_ *T~max~* (at weekly or monthly resolution, as described above) were assessed using a linear mixed model in a hierarchical Bayesian framework.
Analyses were run for both *T~max~* and *T~min~*, with qualitatively similar results, but we present only results for *T~max~*, which had overall stronger correlation with growth parameters. 
Mixed effects models were used to test the response of growth parameters to fixed effects of xylem porosity and mean *T~max~* (or *T~min~*) during the _CTW_, along with random effects of species and of individual tree. 
We ran separate models for each site, and for the response of all growth parameters to *T~max~* (or *T~min~*). 
This mixed-effect model was run within a hierarchical Bayesian framework and fit using the `rstanarm` version 2.21.3 R interface to the Stan programming language (source code available at https://github.com/EcoClimLab/growth_phenology#steps-to-replicate-the-analysis)[@gabry_rstanarm_2020;@standevelopmentteam_stan_2019]. 
In all cases unless otherwise specified, all prior distributions are set to be the weakly informative defaults. 
<!--
More information on rstanarm's default weakly informative priors:
https://cran.r-project.org/web/packages/rstanarm/vignettes/priors.html#default-weakly-informative-prior-distributions
-->
